Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-09-18 ICLR25/formula.tex
update formula.tex

Our observation (by experiments) is that \begin{align*}
	I_X \approx \sum_{b\in X} I_b.
\end{align*} Separately, if all nodes in $X$ are from the layer before $a$, then in experiments, we observe that

\begin{align}
	|(I_X - \sum_{b\in X} I_b)/I_X| << 1. \ (\text{in experiments})
\end{align} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.

@@

For one layer before the target layer, it is very simple and most accurate.

Suppose $b$ is a node in one layer before $a$. To estimate $I_b$, first we need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.

\begin{definition}
	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}$.	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align}
		I_b \approx W_{ba}(v(\hat{b})-\ReLU(v(b))).
	\end{align}

	Specially, if $v(\hat{b})=\ReLU(v(b))$, then we can prove \begin{align*}
		I_b = W_{ba}(v(\hat{b})-\ReLU(v(b))) = 0.
	\end{align*}

@@

Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $v(\hat{b})$ to $\ReLU(v(b))$ is the major source of improvement.

>>>>

Our observation (by experiments) is that \begin{align}
	I_X \approx \sum_{b\in X} I_b.
\end{align} Separately, if all nodes in $X$ are from one layer before $a$, then in experiments, we observe that

\begin{align}
	|(I_X - \sum_{b\in X} I_b)/I_X| < 1\%. \ (\text{in experiments})
\end{align} Even $X$ contains nodes from 3 layers before the target layer, in experiments, $I_X$ is still close to $\sum_{b\in X} I_b$.

@@

For one layer before the target layer, the formula is simple and most accurate. Suppose $b$ is a node in one layer before $a$. To estimate $I_b$, first we need to run $M^a_{\emptyset}$ to compute the upper bound of $a$  to obtain the solution data. Especially, we will read the values of $b$, before $\ReLU$ function and after $\ReLU$ function.

\begin{definition}
	Let $v(b)$ be the value of $b$ in the LP solution of upper bound of $a$, and $v(\hat{b})$ be the value of $\hat{b}=\ReLU(b)$.	Then the formula to estimate improvement of upper bound of $b$ is: \begin{align}
		I_b \approx W_{ba}(v(\hat{b})-\ReLU(v(b))).
	\end{align}

	Specially, if $v(\hat{b})=\ReLU(v(b))$, then we will have \begin{align*}
		I_b = W_{ba}(v(\hat{b})-\ReLU(v(b))) = 0.
	\end{align*}

@@

Of course changing other variables may also effect the upper bound, but our experiments show that, the change from $v(\hat{b})$ to $\ReLU(v(b))$ is the major part of improvement.
